From Reversible Programs to \\ Univalent Universes and Back

### 2021-07-09 Pi+/paper/finite.tex
Footnote

% What now?
In order to study syntactic descriptions of permutations, we will hit the problem of deciding whether two descriptions
refer to the same permutation -- in group theory, this is the \emph{word problem} for $\Sn$. Putting it in this form
allows us to connect it to the broader scope of computational group theory and combinatorics -- we can borrow ideas such
as Coxeter relations and Lehmer codes.

>>>>

% What now?
In order to study syntactic descriptions of permutations, we will hit the problem of deciding whether two descriptions
refer to the same permutation -- in group theory, this is the \emph{word problem} for $\Sn$. Putting it in this form
allows us to connect it to the broader scope of computational group theory and combinatorics -- we can borrow ideas such
as Coxeter relations and Lehmer codes.~\footnote{The concepts we use can be found in any standard textbook on group
theory, or see~\cite{symmetryBook2021} for a univalent point of view.}
